No-click browsing of large hierarchical data

### 2020-05-29 paper/HCC2020-short/paper.tex
...

\begin{abstract}
We introduce a simple interaction technique for finding and browsing
data in a large hierarchical database using only two keys.

@@

Huge amount of movies, musics, and other programs are available on the web, but
finding and viewing a program is not easy because
(1) finding a program takes time, and
(2) a ``confirm'' operation (clicking something or typing a key)
is required for viewing the content.
%
The confirm operations was not required on old TVs and radios,
because we could enjoy TV/radio programs
as soon as we rotated a TV channel dial or a tuning dial of the radio.
%
It is always convenient to view the contents of the selected item
as soon as we find it.
We call such viewing style as ``\textbf{\tit{no-click browsing}}''.

We can use no-click browsing on the ``column view'' mode of Finder.app on MacOS.
In the column view mode, 
the contents of the file is shown at the right side of the window
as soon as we select a file in a folder (Figure \ref{noclickfinder}).
When we type an arrow key and select another file,
the contents is shown instantly without a confirm operation.

@@

We can use no-click browsing on old TVs and radios because the number of
broadcast channels are limited.
Likewise, no-click browsing on Finder.app is useful
when the number of files in a folder is not very large.

No-click browsing is not popular on conventional GUI of personal computers.
People are used to click-based browsing on web browsers and other
information visualization systems.
People can navigate through a huge information space by
clicking links, zooming and scrolling by dragging, and using other GUI techniques.
These techniques are useful for finding an item in a large information space,
but many clicks and drag operations are required,
and the contents of the items are usually not shown during the search.

It would be better
if we could perform the navigation task using devices that have only two keys.
%
We have developed a new navigation technique called ``{Gear}'' for no-click browsing,
where users can explore a large hierarchical database by using only two keys.

@@

Interaction with Gear is based on the following simple principles.
Two types of operations,
{\up} (up) and {\down} (down), are used for the navigation.

@@

\begin{figure}[H]
  \centerline{\includegraphics[width=60mm,bb=0 0 490 490]{figures/fig1.pdf}}
  \caption{Sample data: shop list of a shopping mall.}
  \label{fig1}
\end{figure}

@@

If the user issues {\down} in Figure \ref{fig4}, the next visible entry
(\tsf{Clothing}) is selected (Figure \ref{fig8}), and then the state changes to Figure \ref{fig9}.

@@

When we list the URLs of Web pages of
movies and musics on a {\SB} page,
we can use {\SC} service
for using the Gear interface to select a program from the
list on {\SB} pages, and automatically play it on the browser.

@@

The average time for finding an entry using Gear was 6.84s,
and the average time using standard \ttt{{\textless}input{\textgreater}} was 4.96s.
It takes about 40\% longer than using conventional method.
The standard deviations were 0.71s and 0.93s, respectively.
%
This is a little bit disappointing,
but we are happy to see that
no-click browsing with Gear is not too slower than
conventional methods.
%
We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}), and
got similar results as App2.

\comment{
4-way navigation is commonly used for exploring hierarchical data structure,
and it is familiar to computer users.
Some mobile phones and PDAs are equipped with a jog dial with a push button,
where the dial is used for choosing an item from the list and 
the push button is used for fixing the selection.
% PowerMate is equipped with a push button which can used for such purposes.
% As far as we know,
All the existing methods require more than 2 keys/buttons, and
to the best of the authors' knowledge,
Gear is the only interaction method for exploring hierarchical data structure
with one rotating device.
}

@@

It seems to be a good idea to use Gear on more conventional visualization techniques like
TreeView\footnote{
  \textsf{http://en.wikipedia.org/wiki/Tree\_view}
}, where 4 keys are used for navigation.
%
We can also use Gear on a 1D zooming system like
LensBar\cite{Masui:1998:LVB:647341.721215},
where pointing devices are mainly used for navigation.

@@

We demonstrated Gear at an exhibition
and asked more than 100 people to try it
(Figure \ref{exhibition}).
%
Since the only thing a user can do with Gear was to rotate a wheel,
users seemed to be able to understand the behavior of Gear with trials and errors.
% 
% a user can use the device and see what happens without thinking about
% other interactions.
% 
Using only one rotating device for data navigation is a new experience for
all the visitors, but the hard restriction of the device seemed to have worked in this case.

\begin{figure}[H]
\centerline{\includegraphics[width=50mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People at the right using a wheel device at an exhibition.}
\label{exhibition}
\end{figure}

@@

We have developed a new simple interaction method ``Gear'' for exploring
a large hierarchical data structure.
A Gear user can easily find an entry in a huge hierarchical database
only by using two keys or a rotating device that can be installed at
wide range of locations where conventional keyboards and switches do not fit.
We are hoping to install various implementations of Gear and try them at
various places like kitchens, restrooms, etc.

>>>>

\begin{abstract}
We introduce a novel simple interaction technique for finding and browsing
data in a large hierarchical database using only two keys.

@@

Huge amount of movies, musics, and other programs are available on the web, but
finding and viewing a program is not easy because
(1) finding a program takes time, and
(2) a ``confirm'' operation (clicking something or typing a key)
is required for viewing the content.
%
The confirm operations was not required on old TVs and radios,
because we could enjoy TV/radio programs
as soon as we rotated a TV channel dial or a tuning dial of the radio.
%
It is always convenient to view the contents of the selected item
as soon as we find it.
We call such viewing style as ``\tit{no-click browsing}''.

We can perform no-click browsing on the ``column view'' mode of Finder.app on
MacOS using four keys.
In the column view mode, 
the contents of the file is shown at the right side of the window
as soon as we select a file in a folder (Figure \ref{noclickfinder}).
When we type an arrow key and select another file,
the contents is shown instantly without a confirm operation.

@@

We could use no-click browsing on old TVs and radios because the number of
broadcast channels were limited.
Likewise, no-click browsing on Finder.app is useful
when the number of files in a folder is not very large.

No-click browsing is not popular on modern GUI of personal computers.
People are used to click-based browsing on web browsers and other
information visualization systems.
People can navigate through a huge information space by
clicking links, zooming and scrolling by dragging, and using other GUI techniques.
These techniques are useful for finding an item in a large information space,
but many clicks and drag operations are required,
and the contents of the items are usually not shown during the search.

It would be better
if we could perform the navigation task using devices that have only two keys.
%
We have developed a new navigation technique called ``\tit{Gear}'' for no-click browsing,
where users can explore a large hierarchical database by using only two keys.

@@

Interaction with Gear is based on the following simple principles.
Two operations,
{\up} (up) and {\down} (down), are used for the navigation.

@@

\begin{figure}[H]
  \centerline{\includegraphics[width=70mm,bb=0 0 490 490]{figures/fig1.pdf}}
  \caption{Sample data: shop list in a shopping mall.}
  \label{fig1}
\end{figure}

@@

If the user issues {\down} in Figure \ref{fig4}, the next visible entry
(\tsf{Clothing}) is selected (Figure \ref{fig8}), and the state changes to Figure \ref{fig9}.

@@

When we list the URLs of Web pages of
movies and musics on a {\SB} page,
we can use {\SC} service
for using the Gear interface to select a program from the
list on {\SB} pages and automatically play it on the browser.

@@

The average time for finding an entry using Gear was 6.84s,
and the average time using standard \ttt{{\textless}input{\textgreater}} was 4.96s.
It takes about 40\% longer than using conventional method.
The standard deviations were 0.71s and 0.93s, respectively.
%
This is a little bit disappointing,
but we are happy to see that
no-click browsing with Gear is not too slower than
conventional methods using four keys.
%
We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}), and
got similar results.

@@

It seems to be a good idea to use Gear on more conventional visualization techniques like
TreeView\footnote{
  \textsf{http://en.wikipedia.org/wiki/Tree\_view}
}, where four keys are used for navigation.
%
We can also use Gear on a 1D zooming system like
LensBar\cite{Masui:1998:LVB:647341.721215},
where pointing devices are mainly used for navigation.

@@

We demonstrated Gear at an exhibition
and asked more than 100 people to try it
(Figure \ref{exhibition}).
%
Since the only thing a user could do with the Gear device was to rotate a wheel,
users seemed to be able to understand the behavior of Gear with trials and errors.
% 
% a user can use the device and see what happens without thinking about
% other interactions.
% 
Although using only one rotating device for navigation was a new experience for the visitors,
they seemed to have felt it natural in a short while.

\begin{figure}[H]
\centerline{\includegraphics[width=60mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People at the right using a wheel device at an exhibition.}
\label{exhibition}
\end{figure}

@@

We have developed a new simple interaction method ``Gear'' for exploring
a large hierarchical data structure.
A Gear user can easily find an entry in a huge hierarchical database
only by using two keys or a rotating device that can be installed at
wide ranges of locations where conventional devices do not fit.
We are hoping to install various implementations of Gear and try them at
various places like kitchens, restrooms, etc.
